IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/formal.tex
Fix dupe
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\subsection{Erasure function}

@@

\subsection{Non-interference}

@@

In general, however, non-interference will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha targetLang| with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
%
%In Section~\toref{} we detail the preceise scheduler for which our
%specification language is TSNI.
%

>>>>

\subsection{Erasure Function}

@@

\subsection{Non-Interference}

@@

In general, however, non-interference will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha targetLang| with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will in general break non-interference~\cite{russo2006securing,BartheRRS07}.
%
%In Section~\toref{} we detail the preceise scheduler for which our
%specification language is TSNI.
%
